The regularity of ODEs and thimble integrals \\ with respect to Borel summation

### 2024-03-28 exp-resurgence.tex
updates

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in\textcolor{red}{\mathcal{J}_\alpha^\theta:=} \alpha + e^{i\theta}[0, \infty)$ its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $b$. 
\end{enumerate}
\textcolor{red}{[add figure]}

The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em asymptotic} to a power series
\begin{equation}\label{series:asymp-defn}
a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
if, along each ray toward $\infty$,
\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(z^{-n}\big) \]
over all orders $n$. We will write
\[ F \sim \sum_{n \geq 0} a_n z^{-n} \]
to denote this relationship.
\end{defn}
\color{RoyalBlue}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}%%\label{series:asymp-defn}
\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $F$ if
\[ \left|F - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\textcolor{magenta}{\Re(z)} \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $F$, namely we will write \[F\sim \sum_{n\geq 1} a_n z^{-n}.\]}
\end{defn}
\color{black}
This definition generalizes straightforwardly to ``fractionally shifted'' power series and trans-monomials.
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em asymptotic} to a fractionally shifted trans-monomial
\begin{equation}\label{trans-monom:asymp-defn}
e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots\right)
\end{equation}
if, along each ray toward $\infty$,
\[ \left|F - e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(e^{-\alpha|z|}\,z^{-\sigma-n}\big) \]
over all orders $n$. We will again use $\sim$ to denote this relationship.
\end{defn}

@@

\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a holomorphic function $F$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-defn} if there is a constant $A \in (0, \infty)$ for which
\[ \left|F - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

@@

You can't be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution. After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them. In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem. The question of how that happens is the starting point for this paper.

@@

and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular.
\par
\end{verify}
We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions. However, this only works when there's a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$. Why?

@@

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
\color{DarkBlue}
\begin{theorem}\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \right] \]
of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of the suitable normalizad formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
With a little more work, encapsulated in Lemma~\textcolor{orange}{?} from Section~\textcolor{orange}{?}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
\begin{theorem}\label{thm:soln_is_asymptotic}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{theorem}
\begin{corollary}\label{cor:soln_borel-reg}
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular.
\end{corollary}
From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$. On the other hand, if you prefer to work formally, you can start from the computation of the Poincar\'{e} solutions and the observation that they are $1$-Gevrey, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability. We do this in Section~\ref{sec:new-summability-proof}.

@@

Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface. If $b \in B$ is non-singular, the frequency domain for $\laplace_{\zeta,b}^\theta$ is $T^*_{\zeta=b} B$. If $b$ is a conical singularity, the frequency domain is more interesting, as we will see in our main example (see Figure \ref{fig:different_fibres}). 
\begin{figure}[ht]
\centering
\basicLaplace
\vspace{1cm}

\phaseSpaceLaplace
\caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane. However, the fiber over a singular point of $B$ has an interesting structure. Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}
    \label{fig:different_fibres}
\end{figure}

We’ll illustrate our main results with detailed treatments of several examples: we’ll mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}. In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).

@@

We thank Maxim Kontsevich, David Sauzin, Fr\'ed\'eric Fauvet, Andrew Neitzke, for fruitful discussions and suggestions. 
%
\section{Historical context}\label{sec:historical-context}
%
\subsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $F$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\renewcommand{\rfiber}{3}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\newcommand{\dis}{1.2}
\begin{fiber}[shade, phase=\phase, dis=\dis]
\genfibercontent[dual]
\draw (0, 0) -- (-\phase:\rshade);
\draw[rotate=-\phase] (\dis, -0.1) -- (\dis, 0.1);
\draw (0, 0) -- (0.75, 0);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\phase:0.5) node[midway, anchor=180-\phase/2] {$-\theta$};
\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$c$};
\end{fiber}
\end{tikzpicture}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$z$};
\end{tikzpicture}
\end{center}
\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} F$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$. 
\begin{center}
\begin{tikzpicture}
\renewcommand{\rfiber}{3}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\newcommand{\radius}{1}
\begin{fiber}
\fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
\genfibercontent
\draw (0, 0) -- (0.75, 0);
\draw[ray] (0, 0) -- (\phase:\rshade);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
\end{fiber}
\end{tikzpicture}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\radius}{1}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\outsize, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\outsize, -\radius) -- cycle;
  \begin{scope}[violet]
    \draw (0, 0) -- (\ang:\outsize);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\ang:0.5) node[midway, anchor=180+\ang/2] {$\theta$};
    %%\begin{scope}[rotate=\ang]
    %%  \draw[dotted] (0, 0) -- (0, -\radius) node[anchor=90+\ang] {$r$};
    %%  \draw (\radius, -0.1) -- (\radius, 0.1);
    %%\end{scope}
    %%\fill (mark) circle (0.05);
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$\zeta$};
\end{tikzpicture}
\end{center}

>>>>

Once you have the formal solution $\series{\Phi}$, you might try to get an actual solution by applying {\em Borel summation}, which turns a formal power series into a function asymptotic to it. Borel summation works in three steps.
\begin{enumerate}
\item Thinking of $z$ as a ``frequency variable,'' we take the Borel transform (also known as formal inverse Laplace transform) of $\series{\Phi}$, producing a formal power series $\series{\phi}$ in a new ``position variable'' $\zeta$.
\item If $\series{\phi}$ has a positive radius of convergence, we say $\series{\Phi}$ is {\em $1$-Gevrey}. We sum $\series{\phi}$ to get a holomorphic function $\hat{\phi}$ on a neighborhood of $\zeta = 0$. Then, by analytic continuation, we expand the domain of $\hat{\phi}$ to a Riemann surface $B$ with a distinguished 1-form $\lambda$---the continuation of $d\zeta$. %\textcolor{orange}{[Nikita has a complementary picture where the Borel plane is the cotangent fiber? Ask more about this.]}
\item Furthermore, if $\hat{\phi}$ grows slowly enough along an infinite ray $\zeta \in\textcolor{red}{\mathcal{J}_\alpha^\theta:=} \alpha + e^{i\theta}[0, \infty)$ its Laplace transform $\hat{\Phi} : = \laplace_{\zeta, \alpha}^\theta \hat{\phi}$ turns out to be a holomorphic function of $z$, well-defined on some sector of the frequency plane. In this case, we say $\tilde{\Phi}$ is {\em Borel-summable}, and we call $\hat{\Phi}$ its {\em Borel sum} at $\alpha$. 
\end{enumerate}
%
%
\begin{figure}[ht]
\centering
\basicLaplace
\caption{\small{On the right, the ray $\mathcal{J}_\alpha^\theta$ in the position domain. On the left, the half plane in the frequency domain, where the Laplace transform $\laplace_{\zeta,0}^\theta \hat{\phi}$ is holomorphic.}}
\end{figure}

The series $\series{\Phi}$ and its Borel sum $\hat{\Phi}$ have a special relationship, which is best described in the language of {\em Gevrey asymptoticity}.
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em asymptotic} to a power series
\begin{equation}\label{series:asymp-defn}
a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
if, along each ray toward $\infty$,
\[ \left|\Phi - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(z^{-n}\big) \]
over all orders $n$. We will write
\[ \Phi \sim \sum_{n \geq 0} a_n z^{-n} \]
to denote this relationship.
\end{defn}
\color{RoyalBlue}
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a power series
\begin{equation}%%\label{series:asymp-defn}
\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots
\end{equation}
is {\em asymptotic} to a holomorphic function $\Phi$ if
\[ \left|\Phi - \left(\textcolor{orange}{a_0}+\frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o_{\textcolor{magenta}{\Re(z)} \to \infty}\big(|z|^{-n}\big) \]
over all orders $n$. \textcolor{magenta}{We will use the symbol $\sim$ to denote the asymptotic of $\Phi$, namely we will write \[\Phi\sim \sum_{n\geq 1} a_n z^{-n}.\]}
\end{defn}
\color{black}
This definition generalizes straightforwardly to ``fractionally shifted'' power series and trans-monomials.
\begin{defn}
On an open, possibly bounded sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em asymptotic} to a fractionally shifted trans-monomial
\begin{equation}\label{trans-monom:asymp-defn}
e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \frac{a_3}{z^3} + \frac{a_4}{z^4} + \ldots\right)
\end{equation}
if, along each ray toward $\infty$,
\[ \left|\Phi - e^{\alpha z} z^{-\sigma} \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_n}{z^n} \right) \right| \in o\big(e^{-\alpha|z|}\,z^{-\sigma-n}\big) \]
over all orders $n$. We will again use $\sim$ to denote this relationship.
\end{defn}

@@

\begin{defn}\label{def:unif-gevrey-asymp}
On an open sector $\Omega$ around $\infty$, a holomorphic function $\Phi$ is {\em uniformly $1$-Gevrey asymptotic} to a power series of the form \eqref{series:asymp-defn} if there is a constant $A \in (0, \infty)$ for which
\[ \left|\Phi - \left(a_0 + \frac{a_1}{z} + \frac{a_2}{z^2} + \ldots + \frac{a_{n-1}}{z^{n-1}} \right) \right| \lesssim \frac{A^n n!}{|z|^n} \]
over all orders $n$ and all $z \in \Omega$. We will use $\lesssim$ throughout the paper to mean ``bounded by a constant multiple of,'' with the same constant over all the specified variables.
\end{defn}
To compare the Borel sum $\hat{\Phi}$ with the original series $\series{\Phi}$, let's take it one more step, sending it back into the world of formal power series by taking its asymptotic expansion.

@@

You can not be sure {\em a priori} that $\hat{\Phi}$ solves your original problem, even if you know that $\series{\Phi}$ is asymptotic to an actual solution. After all, $\series{\Phi}$ is asymptotic to lots of functions; Borel summation just picks one of them. In many cases, however, Borel summation picks correctly, delivering an actual solution to your problem. The question of how that happens is the starting point for this paper.

@@

and $-w^{-2}B(1/w)$ has a simple pole at $w=0$ (i.e. $z=\infty$). Then the formal system of solutions is of the form 
\[\psi_j(w)=e^{-\alpha_j/w} w^{\tau_j} \tilde{f}_j(w)\]
hence according to \cite[Definition 3.3.2]{diverg-resurg--ii}, $w=0$ is irregular.
\par
\end{verify}
We can find holomorphic solutions of the equation $\mathcal{P}\Phi = 0$ by taking the Borel sums of formal trans-monomial solutions. However, this only works when there is a coincidence between exponential factor $e^{-\alpha z}$ in the formal solution, the base point $\zeta = \alpha$ we use for Borel summation, and the characteristic equation $P(-\alpha) = 0$. Why?

@@

Furthermore, when $-\alpha$ is a root of $P$, the integral equation $\hat{\mathcal{P}}_\alpha \phi = 0$ has a special solution $\psi_\alpha$ which is distinguished, up to scaling, by its power-law asymptotics at $\zeta = \alpha$~\cite[Theorem~4]{reg-sing-volterra}. This solution is regular enough to have a well-defined Laplace transform $\Psi_\alpha$, which is a special solution of $\mathcal{P}\Phi = 0$ distinguished by its own characteristic asymptotics.
%
\begin{theorem}\label{thm:exist_uniq_ODE}
Let $-\alpha$ be a root of $P$. Consider an open sector $\Omega_\alpha$ which has an opening angle of $\pi$ or less, has $\zeta = \alpha$ at its tip, and doesn't touch any other root of $P(-\zeta)$. The equation $\mathcal{P}\Psi = 0$ has a unique solution $\Psi_\alpha$ in the affine subspace
\[ e^{-\alpha z} \left[ z^{-\tau_\alpha} + \dualsingexpalg{-\tau_\alpha-1}(\Omega_\alpha) \right] \]
of the space $e^{-\alpha z} \dualsingexpalg{-\tau_\alpha}(\Omega_\alpha)$ from Section~\ref{sec:reg-decay}.
\end{theorem}
The special solution $\psi_\alpha$ is also regular enough to have a ``fractionally shifted'' power series expansion $\series{\psi}_\alpha$, whose formal Laplace transform $\series{\Psi}_\alpha$ is a formal solution of $\mathcal{P}\series{\Phi} = 0$. By construction, $\series{\Psi}_\alpha$ is Borel summable, with Borel sum $\Psi_\alpha$.
\begin{theorem}\label{thm:soln_is_Borel_sum}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is the Borel sum of the suitable normalizad formal trans-monomial solution $\series{\Psi}_\alpha \in e^{-\alpha z} z^{-\tau_\alpha}\,\C \llbracket z^{-1} \rrbracket$ of the equation $\mathcal{P}\series{\Phi} = 0$.
\end{theorem}
With a little more work, encapsulated in Lemma~\ref{lem:shifted_holo_closed} from Section~\ref{sec:bridging}, we can use this result to show that $\Psi_\alpha$ is Borel regular.
\begin{theorem}\label{thm:soln_is_asymptotic}
The analytic solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is asymptotic to the formal solution $\series{\Psi}_\alpha$ from Theorem~\ref{thm:soln_is_Borel_sum}.
\end{theorem}
\begin{corollary}\label{cor:soln_borel-reg}
The solution $\Psi_\alpha$ from Theorem~\ref{thm:exist_uniq_ODE} is Borel regular.
\end{corollary}
\begin{remark}
Notice that the result of Theorem~\ref{thm:soln_is_asymptotic} is not a consequence of the general result that the Borel--Laplace sum of 1-Gevrey series $\series{\Phi}$ is uniform Gevrey asymptotic to $\series{\Phi}$ itself (see Theorem~5.20 in~\cite{diverg-resurg-i}). 
\end{remark}
From an analytic perspective, Theorem~\ref{thm:soln_is_Borel_sum} justifies the ansatz that Poincar\'{e} used to solve the equation $\mathcal{P}\series{\Phi} = 0$. On the other hand, if you prefer to work formally, you can start from the computation of the Poincar\'{e} solutions and the observation that they are $1$-Gevrey, and then use Theorem~\ref{thm:exist_uniq_ODE} to establish their Borel summability. We do this in Section~\ref{sec:new-summability-proof}.

@@

Furthermore, we introduce a geometric picture where the position domain $B$ is a translation surface. If $b \in B$ is non-singular, the frequency domain for $\laplace_{\zeta,b}^\theta$ is $T^*_{\zeta=b} B$. If $b$ is a conical singularity, the frequency domain is more interesting, as we will see in our main example (see Figure \ref{fig:different_fibres}). 
\begin{figure}[ht]
\centering
\phaseSpaceLaplace
\caption{The fiber over an ordinary point of the translation surface $B$ is a copy of the complex plane. However, the fiber over a singular point of $B$ has an interesting structure. Here we represent the example of Airy functions, where the singularity as angle $6 \pi$.}
    \label{fig:different_fibres}
\end{figure}
We will illustrate our main results with detailed treatments of several examples: we will mostly focus on degree two ODEs that admit a frame of solutions expressed as thimble integrals: the Airy--Lucas functions (Section~\ref{example_AL}), the modified Bessel functions, the Airy function (Appendix~\ref{airy-appendix}), \textcolor{red}{the anharmonic oscillator...).} On the one hand, we explicitly solve the integral equation associated with the ODE, building a frame of analytic solutions which are Laplace transforms. On the other hand, our \textit{thimble projection reasoning} shows how to rewrite explicitly thimble integrals as a Laplace transform and it makes Borel regularity evident directly from explicit computations. The thimble projection reasoning is the one we use in Lemma~\ref{lem:thimble_proj_formula} and it is crucial for the proof of Theorem~\ref{thm:maxim}. In the Airy example (see Section~\ref{airy-appendix}) we’ll compute the \textit{thimble projection formula} directly, and by numerical check we show $\hat{\phi}\defeq\fracderiv{-1/2}{\zeta}{\alpha}\iota$ is a simple resurgent function (see Section~\ref{apx:eye-res-airy}).

@@

We thank Maxim Kontsevich, David Sauzin, Fr\'ed\'eric Fauvet, Andrew Neitzke, for fruitful discussions and suggestions. 
%
\section{Historical context}\label{sec:historical-context}
%
\subsection{Borel regularity as a good approximation condition}
Borel regular functions can be characterized as functions that are approximated well, asymptotically, by polynomials. Watson showed a century ago \cite[Part II, Section 9]{watson2} that a function $\Phi$ is Borel regular whenever its asymptotic expansion for large $|z|$ is uniformly $1$-Gevrey-asymptotic in an obtuse-angled sector at infinity (see Definition~\ref{def:unif-gevrey-asymp}).

Watson's theorem was soon improved by Nevanlinna \cite{nevanlinna} (see a modern proof in \cite[Theorem~B.15]{nikolaev2023exact} and a generalization to power series with fractional power exponents in \cite{delabaere--rosoamanana}), and improved again later by Sokal \cite{sokal1980improvement}. These improvements tell us that the obtuse-angled sector around $\infty$ in the statement above can be replaced with an open disk whose boundary touches infinity---that is, an half-plane which doesn't contain $0$, and may be displaced from $0$ by some distance $c$.
\begin{center}
\begin{tikzpicture}
\renewcommand{\rfiber}{3}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\newcommand{\dis}{1.2}
\begin{fiber}[shade, phase=\phase, dis=\dis]
\genfibercontent[dual]
\draw (0, 0) -- (-\phase:\rshade);
\draw[rotate=-\phase] (\dis, -0.1) -- (\dis, 0.1);
\draw (0, 0) -- (0.75, 0);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\phase:0.5) node[midway, anchor=180-\phase/2] {$-\theta$};
\node[anchor=90-\phase, inner sep=2mm] at (-\phase:\dis) {$c$};
\end{fiber}
\end{tikzpicture}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\dis}{1.2}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=-\ang] (\dis, -\outsize) rectangle (\outsize, \outsize);
  \begin{scope}[violet]
    \draw (0, 0) -- (-\ang:\outsize);
    \draw[rotate=-\ang] (\dis, -0.1) -- (\dis, 0.1);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:-\ang:0.5) node[midway, anchor=180-\ang/2] {$-\theta$};
    \node[anchor=90-\ang, inner sep=2mm] at (-\ang:\dis) {$c$};
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$z$};
\end{tikzpicture}
\end{center}
\textcolor{orange}{[move $z$, $\zeta$ before removing old purple figures]} When the half-plane extends along the $-\theta$ direction, the sum $\hat{f}$ of the Borel transform of $\aexp^{-\theta} \Phi$ has an absolutely convergent Laplace transform along the $\theta$ direction. In fact, we have $|\hat{f}| \lesssim e^{c |\zeta|}$ uniformly over all $\zeta$ in a constant-radius neighborhood of the ray $e^{i\theta}[0, \infty)$. 
\begin{center}
\begin{tikzpicture}
\renewcommand{\rfiber}{3}
\pgfmathsetmacro{\rshade}{1.5*\rfiber}
\renewcommand{\phase}{35}
\newcommand{\radius}{1}
\begin{fiber}
\fill[pwbeige!30, rotate=\phase] (\rshade, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\rshade, -\radius) -- cycle;
\genfibercontent
\draw (0, 0) -- (0.75, 0);
\draw[ray] (0, 0) -- (\phase:\rshade);
\draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\phase:0.5) node[midway, anchor=180+\phase/2] {$\theta$};
\end{fiber}
\end{tikzpicture}
\begin{tikzpicture}
\newcommand{\size}{3}
\pgfmathsetmacro{\outsize}{sqrt(2)*\size}
\newcommand{\ang}{35}
\newcommand{\radius}{1}
\begin{scope}
  \clip (-\size, -\size) rectangle (\size, \size);
  \fill[violet!20, rotate=\ang] (\outsize, \radius) -- (0, \radius) arc (90:270:\radius) -- (0, -\radius) -- (\outsize, -\radius) -- cycle;
  \begin{scope}[violet]
    \draw (0, 0) -- (\ang:\outsize);
    \draw[shorten <=0.3mm, shorten >=0.3mm] (0:0.5) arc (0:\ang:0.5) node[midway, anchor=180+\ang/2] {$\theta$};
    %%\begin{scope}[rotate=\ang]
    %%  \draw[dotted] (0, 0) -- (0, -\radius) node[anchor=90+\ang] {$r$};
    %%  \draw (\radius, -0.1) -- (\radius, 0.1);
    %%\end{scope}
    %%\fill (mark) circle (0.05);
  \end{scope}
\end{scope}
%%\begin{scope}[violet]
%%  \draw (0, 0) -- (center);
%%  \fill (center) circle (0.05);
%%\end{scope}
\draw[->] (-\size, 0) -- (\size, 0);
\draw[->] (0, -\size) -- (0, \size);
\node[anchor=north west] at (-\size, \size) {$\zeta$};
\end{tikzpicture}
\end{center}
